\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{xcolor}

\title{Stock Trading Portfolio}
\date{}

\begin{document}

\maketitle

\section*{Project Overview}

Welcome to the \textbf{Stock Trading Portfolio} project! This website allows users to buy and sell stocks and is being developed as part of the ITW project at \textbf{IIT (BHU)} by \textbf{Atul Kumar Pandey} and \textbf{Chukka Chamantej}. The backend is powered by \textbf{Django}, and the project includes a machine learning-based recommendation system to enhance the user experience. Our long-term goal is to evolve this platform into a full-fledged algorithmic trading solution.

\section*{Features}
\begin{itemize}
    \item \textbf{User-friendly interface} for stock trading.
    \item \textbf{Machine Learning-based recommendation system} to assist users in making informed trading decisions.
    \item \textbf{Future Goals}: Convert the platform into an algorithmic trading system.
\end{itemize}

\section*{Getting Started}

To get started with this project, follow the instructions below.

\subsection*{Prerequisites}
\begin{itemize}
    \item \textbf{Python} (ensure it's installed on your system)
    \item \textbf{Django} framework
\end{itemize}

\subsection*{Installation Instructions}
\begin{enumerate}
    \item Clone this repository to your local machine:
    \begin{verbatim}
    git clone https://github.com/Atul625-py/Stock_Trading_Portfolio.git
    \end{verbatim}

    \item Navigate to the project directory:
    \begin{verbatim}
    cd Stock_Trading_Portfolio
    \end{verbatim}

    \item Install the required dependencies:
    \begin{verbatim}
    pip install -r requirements.txt
    \end{verbatim}

    \item Run the Django server:
    \begin{verbatim}
    python manage.py runserver
    \end{verbatim}
\end{enumerate}

\section*{Contributing}

We welcome contributions to improve the project. Feel free to fork the repository, make your changes, and submit a pull request.

\section*{Future Plans}
\begin{itemize}
    \item Expand the functionality to include \textbf{algorithmic trading} capabilities.
    \item Integrate more advanced machine learning algorithms for better recommendations.
\end{itemize}

\section*{License}

This project is licensed under the MIT License. See the \href{LICENSE}{LICENSE} file for details.

\end{document}
